\tool

### 2018-02-21 paper/paper.tex
Updating tool description intro

\section{Tool}
Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.

>>>>

\section{Tool}
\tool aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our system for making recommendations similar to those from a peer and incorporating software engineering industry practices.
